---
title: "2023_ple.27.7e_assessment"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plaice (_Pleuronectes platessa_) in Division 7.e (western English Channel) - WGCSE 2023 (update only, no new advice!).

This repository recreates the stock assessment for plaice (_Pleuronectes platessa_) in Division 7.e (western English Channel) in `R` from WGCSE 2023.

The advice for this plaice stock is biennial and was last given one year ago at WGCSE 2022. This repository is only a data update and does not calculate a new advice value.

## R packages 

The following R packages from CRAN are required to run the assessment:

```{r, eval = FALSE}
TAF
```

They can be installed with:
```{r, eval = FALSE}
### list with required packages
req_pkgs <- c("TAF")
### install/update packages
install.packages(req_pkgs)
```

Furthermore, the following packages from GitHub are required:
```{r, eval = FALSE}
cat3advice
```
For exact reproducibility, it is recommended to use exactly the same package version as used in the assessment. These package are automatically installed into a local library when running the TAF assessment (see below) or by calling
``` {r, eval = FALSE}
taf.boot()
```
Alternatively, they can be manually installed from GitHub with
``` {r, eval = FALSE}
TAF::taf.libPaths() # install packages into local TAF library
remotes::install_github("shfischer/cat3advice")
```
## Running the assessment

The easiest way to run the assessment is to clone or download this repository, navigate into the repository with R and run:
```{r, eval = FALSE}
### load the icesTAF package
library(TAF)
### load data and install R packages
taf.boot()
### run all scripts
sourceAll()
```

This code snippet runs the data compilation and assessment and creates the tables and figures presented in the WG report.

